---
title: "Simple Presentation of Iowan Recidivism"
author: "Jarren Santos"
date: "4/30/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("~/Documents/Grinnell College/04_Spring 2017/MAT-397 (Adv Data Sci)/Coursera/08_Developing Data Products/DDP-Week-03/")
prison <- read.csv("prison_clean.csv")
```


## Background

Recidivism occurs when a prisoner is released from jail, relapses back into criminal behavior, and is rearrested.

Understanding what prisoner traits are associated with rearrest after release (known as recidivism) is vital for the successful and effective implementation of assistance programs aimed at preventing recidivism.


## Data Source

The data are openly available through the government: https://data.iowa.gov/Public-Safety/3-Year-Recidivism-for-Offenders-Released-from-Pris/mw8r-vqy4

We use a previously cleaned version of the data to demonstrate basic data visualization.  Summaries for data input were calculated beforehand.


## Interactive Data Visualization: Plotly

```{r, warnings = FALSE, message = FALSE, warning = FALSE}
plotly::plot_ly(x = c("Criminals Return to Jail", "Criminals Stay Out of Jail"), y = c(5128, 11370), name = "Count of Prisoner Recidivism", type = "bar")
```


## Interactive Data Visualization: Google Vis

```{r setOptions, message = FALSE}
suppressPackageStartupMessages(library(googleVis))
op <- options(gvis.plot.tag='chart')
```

```{r gv, results = "asis", tidy = FALSE, warning = FALSE}
prison1 <- data.frame(c("Criminals Return to Jail", "Criminals Stay Out of Jail"), c(5128, 11370))
M <- gvisBarChart(prison1)
plot(M)
```

